Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2009-02-18 presentation/presentation.out.tex
commit to topics drawing fucking with sizing and everything

\begin{center}
\includegraphics[width=\textwidth]{transitiveclosure}
Clustering topics (black dots) by Transitive Closure based on similarity (arcs)
\end{center}

@@

\begin{table*}
\centering
\begin{tabular}{|ccc|l|}

@@

2001 &	Aug &	25 &		tables row version [a] \\
\hline
%2001 &	Sep &	24 &		update checksum merge \\
%2001 &	Oct &	24 &		fixed fix \\
%2001 &	Dec &	23 &		HPUX SCO fix \\
\hline
2002 &	Feb &	21 &		net buffer length	max\_allowed\_packet [b] \\
2002 &	Mar &	23 &		small buf fix [b]	\\
%\hline
%2002 &	May &	22 &		[popular] fix SCO OSF1 table\_name \\
%2002 &	Nov &	18 &		HPUX11 compiler HP \\
\hline
\hline
2003 &	Feb &	16 &		Linux errno	[c] \\
2003 &	Mar &	18 &		alarm bookmark bug [c] \\
%\hline
%2003 &	Sep &	14 &		Auto logging merge windows distribution fix 64-bit 4.0 Cleanup \\
\hline
\end{tabular}
\caption{Continuous blocks found while tracking topics associated with the word portability in MySQL 3.23}
\label{tab:portability}
\end{table*}

@@

\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}

>>>>

% \begin{center}
% \includegraphics[width=\textwidth]{transitiveclosure}
% Clustering topics (black dots) by Transitive Closure based on similarity (arcs)
% \end{center}

%\igninetycap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}
\igonecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

@@

%\begin{table*}
\begin{specquotef}
\centering
\begin{tabular}{|ccc|l|}

@@

2001 &	Aug &	25 &		tables row version [a] \\
\hline
%2001 &	Sep &	24 &		update checksum merge \\
%2001 &	Oct &	24 &		fixed fix \\
%2001 &	Dec &	23 &		HPUX SCO fix \\
\hline
2002 &	Feb &	21 &		net buffer length	max\_allowed\_packet [b] \\
2002 &	Mar &	23 &		small buf fix [b]	\\
%\hline
%2002 &	May &	22 &		[popular] fix SCO OSF1 table\_name \\
%2002 &	Nov &	18 &		HPUX11 compiler HP \\
\hline
\hline
2003 &	Feb &	16 &		Linux errno	[c] \\
2003 &	Mar &	18 &		alarm bookmark bug [c] \\
%\hline
%2003 &	Sep &	14 &		Auto logging merge windows distribution fix 64-bit 4.0 Cleanup \\
\hline
\end{tabular} \\
%\caption{Continuous blocks found while tracking topics associated with the word portability in MySQL 3.23}
{Continuous blocks found while tracking topics associated with the word portability in MySQL 3.23}
\label{tab:portability}
%\end{table*}
\end{specquotef}

@@

%\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}
%\igonecap{lda}{Example of topics extracted from MySQL 3.23}
%\igbigcapb{lda}{Example of topics extracted from MySQL 3.23}
%\igbigthirtycapb{lda}{Example of topics extracted from MySQL 3.23}
\igbigthirtyfivecapb{lda}{Example of topics extracted from MySQL 3.23}
